The pollination trade-off

### 2018-11-27 paper/manuscript.Rmd
Add paragraph of conspecific bagged vs open flowers

>>>>

We then compared the amount of conspecific pollen deposited on flowers open to animal-mediated pollinators and those that were closed. 
We found that, generally most species had more conspecific pollen deposited in their stigmas when animal-mediated pollination took place, although for most species the difference was not significant at the 0.05 level (Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c). 
Specifically, the difference weas non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of species in a community, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open.
